---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# pets

<!-- badges: start -->
<!-- badges: end -->

# Background

The `{pets}` package was designed to allow people to express their feelings about pets. At present, the package is rather cat-centric, in that it only contains one function: `cats()`.

# Usage

To use `{pets}`, first load the package and then call the function `cats()` with a logical/boolean argument. For example, 

```{r setup}
## load pets package
library(pets)

## if you love cats
cats(TRUE)

## if you're not a big fan of cats
cats(FALSE)
```

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("markusmin/pets")
```

## Error reporting

If you find an error or bug, please file an issue.

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(pets)
## basic example code
```


